|

### 2018-12-13 Paper 2019.Rmd
Adding notes from conversation with Erin

```{r post-Lentz panel effects modeling, eval=F}
# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")

CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
CCIDID03 <- lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)

```{r post-Lentz DID effects modeling, eval=F}
# From Erin: 
# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
```

@@

<!--Add in summary statistics here. 
Plot of something over time?
Histograms?
-->
```{r Barber summary, eval=TRUE}
descr(Barber)
# Barber histograms 
ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
ind_limits_2010.plot
ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
ind_limits_2010.plot
pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()
```

@@

@@

The fourth data set provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization. Alt and Lassen's data set runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004.

<!--Describe controls here, then add a table with summary statistics for everything-->

@@

@@

@@

>>>>

@@

<!--Add in summary statistics here. 
Plot of something over time? Histograms? Correlations? 
-->
```{r Barber summary, eval=TRUE}
descr(Barber)
# Barber histograms 
ind_limits_2010.plot <- ggplot(Barber, aes(ind_limits_2010)) + geom_density() + theme_minimal()
ind_limits_2010.plot
ind2pty_limits_2010.plot <- ggplot(Barber, aes(ind2pty_limits_2010)) + geom_density() + theme_minimal()
ind_limits_2010.plot
pac_limits_2010.plot <- ggplot(Barber, aes(pac_limits_2010)) + geom_density() + theme_minimal()

# Correlation matrix? 
pairs(Barber[3:7])
# Doesn't make sense, because of use of 99,999s. 
```

@@

<!--clean these up-->

@@

```{r CCI and CRI correlations }
ggplot(BarberICC, aes(CCI,CRI)) + geom_point() + theme_minimal() + geom_abline()
```

The fourth data set provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A). Alt and Lassen's data set runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004.

@@

```{r post-Lentz panel effects modeling, eval=F}
# Include lagged dependent variables here. 
# Erin's question: Are these "pooled"? 
# Her effort to understand: Write out the formulas. 
# Maybe helpful? https://onlinecourses.science.psu.edu/stat502/node/162/
# Erin's suggestion https://www.princeton.edu/~otorres/Panel101R.pdf
# On robust standard errors https://stats.stackexchange.com/questions/117052/replicating-statas-robust-option-in-r
# And https://cran.r-project.org/web/packages/sandwich/vignettes/sandwich.pdf
# And https://www.brodrigues.co/blog/2018-07-08-rob_stderr/, 
# Pretty good explanation here https://www.methodsconsultants.com/tutorial/introduction-to-random-effects-models-including-hlm/
# Go through this? https://github.com/tyleransom/EconometricsLabs/blob/master/tidyRcheatsheet.pdf
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within", effect="twoways"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="within"))
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), model="random")) #FAIL 
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="pooling")
summary(plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC), model="within")

@@

CCIDID01 <- lm(CCI ~ ind_dummy_f*ind_d, data = DiDsmall)
# Erin: What this doesn't have is an average treatment effect. So add the interaction of the dummy variable of the change having happened and the law occurring. Time dummy, maybe? 
CCIDID02 <- lm(CCI ~ pac_dummy_f*pac_d, data = DiDsmall)
CCIDID03 <- lm(CCI ~ ind2pty_dummy_f*ind2pty_d, data = DiDsmall)

```{r post-Lentz DID effects modeling, eval=F}
# From Erin: 
# •	Again, writing out a model for the D-in-D in Table 4 might help readers to understand what is being isolated. Right now, I’m not sure I fully follow the estimation choices.
# o	At a minimum, the state-level control variables changed during this time (and hence wouldn’t get differenced out), and ought to be included.
# o	Column 1 (and 2): the large standard errors on individual limits removed and imposed suggest multicollinearity and needs to be investigated. 
# Are presence of campaign finance laws in a state year associated with a different level of corruption? No, according to that panel model. 
# Consider adding state fixed effects to the DiD model, for robustness. 
```

@@

\newpage
##Appendix A: Descriptions of Control Variables
In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:
